---
title: "Pairs Exploration"
author: "Zarni Htet"
output: github_document
---

### Libraries 

```{r, R.options= "false"}
require(rio) #for importing data
require(bit64) #for integer values
```

## Census Tract-BID Data

### Importing Cleaned Census Tract/BIDs data
```{r}
All_BIDS <- import("data/intermediate/CT_BIDs_Full.dta")
```

### Exploring the cleaned data
```{r}
head(All_BIDS)
```

### Checking out the Number of BIDS based on name
```{r}
length(unique(All_BIDS$BID_name))
head(All_BIDS$BID_name)
```

### Checking out the Number of BIDS based on ID
```{r}
length(unique(All_BIDS$BID_id))
head(All_BIDS$BID_id)
```

### General Clarification Comments

1. The BIDS ID and the BID Names are the same but with Zeros being stripped?
2. The characteristics of the Census tract right now is its area & borough? These will be joined with more census tract characteristics?
3. What is Census Tract weight?


## BiDs Data

### Importing BiDs data
```{r}
bidsmerged <- import("data/processing/BiDsMerged.csv")
```

### Initial Exploration
```{r}
head(bidsmerged)
```

### Things to Do

1. Fill in the NAs of No. Block Faces Covered and No. Ground Floor Retail Businesses using
https://www1.nyc.gov/site/sbs/neighborhoods/bid-directory.page?bid=30

2. Separate out the Organization Year Variable

3. Clean Zipcode

4. Convert dollar signs to integers
