---
title: "Pairs Exploration"
author: "Zarni Htet"
output: github_document
---

### Libraries 

```{r, R.options= false}
require(rio) # for importing data sets
require(bit64) # for integer values later on
```


## CT_Bids Full

### Importing cleaned data
```{r}
All_BIDS <- import("../data/intermediate/CT_BIDs_Full.dta")
```

### Exploring the cleaned data
```{r}
head(All_BIDS)
print(dim(All_BIDS))
```

### Checking out the Number of BIDS based on name
```{r}
length(unique(All_BIDS$BID_name))
head(All_BIDS$BID_name)
```

### Checking out the Number of BIDS based on ID
```{r}
length(unique(All_BIDS$BID_id))
head(All_BIDS$BID_id)
```

## Bids Merged Data

### Importing BiDs Merged Data
```{r}
bidsmerged <- import("../data/processing/BiDsMerged.csv")
```

### Exploring BiDs data
```{r}
head(bidsmerged)
```

### Things to do with BiDs Merged

1. Fill the missing org_blocks and org_businesses using
https://www1.nyc.gov/site/sbs/neighborhoods/bid-directory.page?bid=30

2. Split the Founding Year variable

3. Fix the Zipcode

4. Fix the dollar sign of assessment



